---
title: "Plot New and Common GN Names"
author: "Shawn Behrend"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
After creation of the gn_all,csv which contains all the gender-neurtal names along with the last year of the decade they are apart of, this CSV is then processed in Microsft Excel. It is sorted by Name and then by year to determine if each anem is new within a decade or was common with the previous decade. AN example is shown here.

Once that is complete, the count of how many names were new per decade versus common with the previous decade was done. THis is shown here.

Next those tallys are plotted per decade.
```{r}
#load data files
new_common_df<-read.csv("C:/Users/shawn/OneDrive/Shawn/CSU_global/MIS581/project_r_code/name_files/gn_all_with_status.csv")
xaxis_labels<-unlist(new_common_df[1])
xaxis<-c(1:length(xaxis_labels))
new<-as.numeric(unlist(new_common_df[2]))
common<-as.numeric(unlist(new_common_df[3]))
total<-as.numeric(unlist(new_common_df[4]))

# x axis for all plots

#plot first data line
plot(xaxis,total,main="Gender Neutral Names: \nTotal Names, New Names and Common Names\nBy Decade: 1880-2020",
     xlab="",xaxt="n",ylab="Number of Names",type="l",lwd=2,col="blue",ylim=c(20,140),cex.main=0.9,cex.axis=0.8)
# plot additional lines
lines(xaxis,new,lwd=3,col="red")
lines(xaxis,common,lwd=3,col="green")
axis(1, at=seq_along(total),labels=as.character(xaxis_labels), las=2,cex=0.6)
# legend
legend("topright",legend=c("Total","New", "Common"),cex=0.6,col=c("blue", "red", "green"),lwd=2,lty=1)
```
